---
title: "Coffee Tasting"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Packages
library(dplyr)
library(ggplot2)
library(knitr)
library(reshape)
library(reshape2)
library(RColorBrewer)
library(GGally)
library(scales)
library(memisc)
library(tidyr)
```

## Load the Data
```{r echo=TRUE, load_data}
ct <- read.csv('/Users/aehsaei/Documents/DataAnalyst/CoffeeTasting/CoffeeTasting.csv', 
               row.names = NULL)
```

## Description
There are many different types of methods to brew coffee. Here are five 
different methods that were used in this test.

#### Pourover
* Pourover coffee starts with (freshly) ground coffee, a filter, and a filter 
holder, often called a 'pourover dripper.' At the most basic level, pourover 
brewing involves pouring water over and through the grounds to extract the 
coffee flavors into your cup or serving vessel.

#### Chemex
* The Chemex Coffeemaker is a manual, pour-over style glass-container coffeemaker 
that Peter Schlumbohm invented in 1941. The Chemex Coffeemaker 
consists of an hourglass-shaped glass flask with a conical funnel-like neck 
(rather than the cylindrical neck of an Erlenmeyer flask) and uses proprietary 
filters, made of bonded paper (thicker-gauge paper than the standard paper 
filters for a drip-method coffeemaker) that removes most of the coffee oils, 
brewing coffee with a taste that is different than coffee brewed in other 
coffee-making systems; also, the thicker paper of the Chemex coffee filters may 
assist in removing cafestol, a cholesterol-containing compound found in coffee 
oils.

#### French Press
* A French press, also known as a cafetière, сafetière à piston, Cafeteria, press 
pot, coffee press, or coffee plunger, is a coffee brewing device patented by 
Italian designer Attilio Calimani in 1929. Coffee is brewed by placing the ground coffee in the empty beaker and adding hot (93-96 degrees Celsius, 200-205 degrees Fahrenheit) water, in proportions of about 30 grams (1 ounce) of coffee grounds to 500 ml (15 fluid ounces) of water, more or less to taste. The brewing time is about two to four minutes. The plunger is pressed to separate the grounds and hold them at the bottom of the beaker. 

#### Tammy Machine
* A mysterious ancient device that uses magic to extract coffee from coffee beans.

#### Miele
* A built-in coffee machine with bean-to cup system.

## Blind Study
We conducted a blind study on 11 participants to determine the most preferred 
coffee brewing method. Each participant was given a coffee by Counter Culture
brand coffee named "La Golondrina" that was brewed 5 different ways as described
above. A 6th brew method was added for comparison that was not the same coffee
and was purchased from Starbucks using Starbucks coffee.

Each participant tried all 6 samples of coffee and rated each based on a 1-5
taste scale. The least preferred taste was a score of 1 and the highest 
preferred taste score was a score of 5.

## Analyze Results
```{r echo=TRUE, analyze_results}
summary(ct)

ct.avg <- ct %>%
  group_by(Coffee) %>%
  summarise(Average.Taste.Score = mean(Taste.Score))

ct.avg
```

## Plot Results
```{r echo=TRUE, plot_results}
ggplot(data = ct.avg, aes(x = Coffee, y = Average.Taste.Score)) +
  geom_bar(stat = "identity", aes(fill = Coffee))
```

## Results
The most preferred brew method was the Miele machine. Here is the ranking in 
order of most to least preferred.

```{r echo=FALSE, ranking}
ct.avg %>%
  arrange(desc(Average.Taste.Score))
```